---
title: "Wine reviews"
author: "mdneuzerling"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)

set.seed(754804) # Chosen by fair dice roll. Guaranteed to be random.
 
library(tidyverse)
library(rvest)
library(kableExtra)
library(e1071)
library(visdat)
library(naniar)
library(tidytext)
library(wordcloud)
data("stop_words")

red_wine_colour <- "#59121C"
white_wine_colour <- "#EADB9F"
rose_wine_colour <- "#F5C0A2"

wine <- "wine_reviews.csv" %>% 
    read_csv %>% 
    mutate(variety = variety %>% tolower)
```

## Incomplete data

From the data visualisation below, we can see that the price data for the wine
is incomplete. Approximately `r round(100 * prop_miss(wine$price))`% of the 
price values are missing. The other missing values are actually empty strings.
Interestingly, a data frame doesn't treat these as missing by default, but a 
tibble does.

```{r vis_dat, cache = TRUE}
wine %>% sample_n(30000) %>% vis_dat
```

One wine, indexed 86909, has a missing variety. Fortunately, we can recover the
information from the review:

```{r missing variety}
wine <- wine %>% mutate(
  variety = ifelse(X1 == 86909, "petite syrah", variety)
)
```

Petite Syrah

## Grape colours

In order to classify the wines as red, white or rosé, we're going to scrape
wine data from the [List of grape varieties](https://en.wikipedia.org/wiki/List_of_grape_varieties)
Wikipedia page, using the `rvest` package. The first three tables of this page
give red, white and rosé wines, in that order.

```{r grape_colours_wiki_scrape, message = FALSE}
wiki_tables <- "https://en.wikipedia.org/wiki/List_of_grape_varieties" %>% 
    read_html %>% 
    html_nodes("table")
red_wines <- wiki_tables[[1]] %>% html_table %>% cbind(colour = "red")
white_wines <- wiki_tables[[2]] %>% html_table %>% cbind(colour = "white")
rose_wines <- wiki_tables[[3]] %>% html_table %>% cbind(colour = "rosé")
all_wines <- rbind(red_wines, white_wines, rose_wines)
```    

We're interested in three columns here: `Common Name(s)`, `All Synonyms` and
the `colour` column we defined from the table scraping. We will take the 
opportunity to rename the columns to match the tidyverse style.

Apart from synonyms, some wines can also have multiple common names, eg. 
"shiraz / syrah". The synonyms seem to be very broad, and can include some
unexpected results: pinot grigio (also known as pinot gris) is used to produce
white wine, yet it appears as a synonym to canari noir, which is used to make
red wine.

We're going to preference the common names over the synonyms, so that in any
conflict we use the colour as given by the common name. To do this, we're going
to `unnest` the common names and clean the results so that all entries are in 
lower-case, the results are distinct, and certain stray bits of punctuation are 
removed. We're then going to do the same with the synonyms, but when we combine
the results we will ignore all entries that are already provided by the common
names.

The end result will be a single table with two columns: `variety`, and `colour`. 
The table may very well still contain duplicates, but certainly less than we 
would have had if we had treated common names and synonyms as equals.

```{r grape_colours_cleaning, message = FALSE}
all_wines_cleaned <- all_wines %>% 
    rename(
        common_names = `Common Name(s)`,
        synonyms = `All Synonyms`
    ) %>% 
    mutate_all(tolower) %>% 
    select(common_names, synonyms, colour)

common_names <- all_wines_cleaned %>%
    unnest(common_names = strsplit(common_names, " / ")) %>% # split common names into separate rows
    rename(variety = common_names) %>% 
    mutate(
        variety = gsub("\\.", "", variety), # remove periods 
        variety = gsub("\\s*\\([^\\)]+\\)", "", variety), # remove brackets and anything within
        variety = gsub("\\s*\\[[^\\)]+\\]", "", variety) # same for square brackets
    ) %>% 
    select(variety, colour)

synonyms <- all_wines_cleaned %>% 
    unnest(synonyms = strsplit(synonyms, ", ")) %>% # split the synonyms into multiple rows
    rename(variety = synonyms) %>% 
    mutate(
        variety = gsub("\\.", "", variety), # remove periods 
        variety = gsub("\\s*\\([^\\)]+\\)", "", variety), # remove brackets and anything within
        variety = gsub("\\s*\\[[^\\)]+\\]", "", variety) # same for square brackets
    ) %>% 
    select(variety, colour) %>% 
    anti_join(common_names, by = "variety") # remove synonyms if we have a common name

variety_colours <- rbind(common_names, synonyms) %>% 
    distinct %>% 
    arrange(variety)
```    

The end result is `r nrow(variety_colours)` rows, with plenty of repeated 
entries to accommodate for multiple names or variations in spelling.

There is an issue here that we haven't confronted: some varieties, especially
those named after regions rather than grapes, can be either red or white. This
leads to 

Now we join the colours with the wine data. If there are any missing values, we 
can attempt to fill them in based on obvious clues in the variety (eg. a "Red 
blend" can safely be assumed to be a red wine). We're going to repeat this
join as we iteratively improve the `variety_colours` data, so we'll define it 
as a function.

```{r join_with_variety_colours}
join_with_variety_colours <- function(wine, variety_colours) {
    wine %>% 
        left_join(
            variety_colours %>% select(variety, colour),
            by = "variety"
        ) %>% 
        mutate(
            colour = case_when(
                !is.na(colour) ~ colour,
                grepl("sparkling", variety, ignore.case = TRUE) ~ "white",
                grepl("champagne", variety, ignore.case = TRUE) ~ "white",
                grepl("red", variety, ignore.case = TRUE) ~ "red",
                grepl("white", variety, ignore.case = TRUE) ~ "white",
                grepl("rosé", variety, ignore.case = TRUE) ~ "rosé",
                grepl("rose", variety, ignore.case = TRUE) ~ "rosé"
            )
        )
}

wine_colours <- wine %>% join_with_variety_colours(variety_colours)

wine_colours %>% 
    count(colour) %>% 
    knitr::kable(format = "html") %>% 
    kable_styling(full_width = F)
```

We still have some colours missing, but first we consider the wines that have
been classified as multiple colours:

```{r wrong_colours}
wine_colours %>% 
    distinct(variety, colour) %>% 
    count(variety) %>% 
    filter(n > 1) %>% 
    knitr::kable(format = "html") %>% 
    kable_styling(full_width = F)
```

We use web searches to manually classify the varieties based on the colour of 
the wine that is most often produced from them.

```{r wrong_colours_fix}
variety_colours <- variety_colours %>% 
    filter(!(variety == "alicante" & colour != "red")) %>%     
    filter(!(variety == "grignolino" & colour != "red")) %>% 
    filter(!(variety == "malvasia fina" & colour != "white")) %>% #rarely red
    filter(!(variety == "sauvignon" & colour != "white"))
```

The below suggests that blends are not being classified:

```{r missing_colours}
wine_colours %>% 
    filter(is.na(colour)) %>% 
    count(variety, sort = TRUE) %>% 
    head(10) %>% 
    knitr::kable(format = "html") %>% 
    kable_styling(full_width = F)
```

We operate under the assumption that if multiple wines are listed, the first
wine determines the colour. For example, cabernet is red and sauvignon is white,
but cabernet sauvignon is red. We try to classify the unclassified wines again
but using only the first word in their varieties. We split the variety by either
spaces or dashes.

```{r blend_classification}
blend_colours <- 
    wine_colours %>% 
    filter(is.na(colour)) %>% 
    select(variety) %>% 
    rowwise %>% 
    mutate(first_variety = unlist(strsplit(variety, "\\-|\\ | "))[1]) %>% 
    merge(variety_colours, by.x = "first_variety", by.y = "variety") %>% 
    select(variety, colour) %>% 
    distinct
```

Now we can rebuild the wine colours using these new blend results:

```{r join_with_blend_colours}
wine_colours <- wine %>% join_with_variety_colours(
    rbind(variety_colours, blend_colours)
) 
```

We manually classify the remaining  `r wine_colours %>% filter(is.na(colour)) %>% distinct(variety) %>% nrow`
varieties using web searches or the `description`s (reviews) associated with
the wines.

```{r manual_colours}
manual_colours <- "manually_classified.csv" %>% read_csv

wine_colours <- wine %>% join_with_variety_colours(
    rbind(variety_colours, blend_colours, manual_colours)
) 

wine_colours %>% 
    count(colour) %>% 
    knitr::kable(format = "html") %>% 
    kable_styling(full_width = F)
```

This is a somewhat aggressive classification. Many varieties, such as the
malvasia fina we encountered earlier, can be used to produce either red or 
white. Dessert wines and orange wines complicate matters even further. There's
also a strong argument to consider sparkling wines as a separate category 
altogether.

## Points

```{r points}
wine_colours %>% ggplot(aes(x = points)) + 
    geom_histogram(
        bins = nrow(wine %>% distinct(points)),
        colour = "white",
        fill = red_wine_colour
    )
```


## Text analysis

Each wine is accompanied by a single-paragraph review. Using the tidytext 
package we can investigate word and n-gram frequency of these reviews. We first
break down the review into single words.

```{r cache = TRUE}
wine_words <- wine %>% 
    unnest_tokens(word, description) %>% 
    anti_join(stop_words, by = "word") %>% 
    filter(word != "wine")
```

We can now generate a simple plot of the ten most commonly occurring words. Some
words, such as "the" and "a", occur frequently and serve only a grammatical
purpose, and so are excluded. We also exclude the word "wine", since the presence
of this word doesn't tell us much about the review.

```{r}
wine_words %>%
    count(word, sort = TRUE) %>%
    head(20) %>%
    mutate(word = reorder(word, n)) %>%
    ggplot(aes(word, n)) +
    geom_col(fill = red_wine_colour) +
    xlab(NULL) +
    theme(text = element_text(size=16)) +
    coord_flip()
```

I'm not sure what purpose word clouds serve, but they seem mandatory at this
point.

```{r}
wine_words %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100))
```

An n-gram is a tuple of words appearing sequentially in order within an 
utterance. For example, in the utterance "My name is Fred", "is Fred" is a 
2-gram and "name is Fred" is a 3-gram. A word could also be considered as a
1-gram. Below we define the 2-grams (bigrams) and 3-grams (trigrams) of the wine 
descriptions. 

Along with the `ngram` column, the `separate` column provides us
with separate columns for each word in the n-gram. The column names for these
words are dynamically generated in the `wine_ngrams` helper function, which
provides outputs a tibble of n-grams for a given n. We then use these new
word columns to filter out the stop words, although this time we include n-grams
with the word "wine".

```{r cache = TRUE}
wine_ngrams <- function(n) {
    wine %>%  
        unnest_tokens(ngram, description, token = "ngrams", n = n) %>% 
        separate(
            ngram, 
            sapply(1:n, function(x) {paste0("word", x)}), # eg, "word1", "word2" 
            sep = " ",
            remove = FALSE # keep the n-gram in the tibble
        )
}

wine_2grams <- wine_ngrams(2) %>% 
    filter(!word1 %in% stop_words$word) %>%
    filter(!word2 %in% stop_words$word)
wine_3grams <- wine_ngrams(3) %>% 
    filter(!word1 %in% stop_words$word) %>%
    filter(!word2 %in% stop_words$word) %>% 
    filter(!word3 %in% stop_words$word)
```

There are `r nrow(wine_2grams)` 2-grams, taking up around 
`r round(as.numeric(object.size(wine_2grams)) / 1024^2)` megabytes of memory, 
and `r nrow(wine_3grams)` 3-grams, taking up around 
`r round(as.numeric(object.size(wine_3grams)) / 1024^2)` megabytes. The drop in
number and size is due to the filtering of the stop words.

We can also plot the frequency of the 2- and 3-grams:

```{r}
plot_ngram_frequency <- function(x) {
    get(paste0("wine_", x, "grams")) %>%
        count(ngram, sort = TRUE) %>%
        head(20) %>%
        mutate(ngram = reorder(ngram, n)) %>%
        ggplot(aes(ngram, n)) +
        geom_col(fill = red_wine_colour) +
        xlab(NULL) +
        theme(text = element_text(size=16)) +
        coord_flip() + 
        ggtitle(paste0("Frequency of ", x, "-grams"))
}

plot_ngram_frequency(2)
plot_ngram_frequency(3)
```








